{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-29 paper/paper.tex
fixed direct citations

The idea is to 'track and regulate' \cite{Zdancewic04} where information flows to
prevent the leak of secret information. The ways on which the information flows
through the system are called channels. Channels that are not indented to transport
information are called covered channels. These covered channels can
be classified into the following categories \cite{Sabelfeld03} (in the following examples $h$ is a secret
variable and $l$ a variable that is plublic):

@@

The notion of confidentiality that is used in most work in the area of information-flow security is \textit{noninterference}.
This policy is defined in various ways but the essence is, that it requires 'that secret information
[do] not affect [the] publicly observable behavior of a system'\footnote{Even wen the attacker has full access to the
source code of the program.}\cite{Zdancewic04}. For most real world
applications this policy is far too strict, because it forbids useful programs like password checkers.\footnote{A
password checker needs to reveal whether the user input was correct or not.} Approaches that allow
controlled release of information are called declassification. The kinds of declassification are \textit{what}
information is released, \textit{who} released this information, \textit{where} in the system the information
is released and \textit{when} the information is released (c.f. \cite{Sabelfeld05}). For these approaches it is necessary that an
active attacker can only know as much as a passive attacker.

@@

The next thing introduced are the security levels. We assume the attacker
'is' a level $k$. From this assumption we can reduce every set of security levels
w.l.o.g into $\{low, high\}$, where $low < high$, by mapping elements
that are no more sensitive than $k$ to $low$ and all other elements
-- including incomparable ones -- to $high$. It is also assumed, that access
control works correctly (i.e. the attacker can not access $high$ elements
directly).

@@

The \textit{hidden} threads are the ones we have to care about. These contain
obviously high information in the current program point, but have afterwards
instructions that deal with low information. Since the attacker can watch the
low part of the memory, chances are good that he can deduce high information
through looking at changing low outputs. To prevent indirect flows that are introduced by
these hidden threads, the scheduler will be modified to treat these threads
in a special way. This will be done by 'hiding' these threads, therefore comes
the name of them.

@@

The security levels in $LType$ are the security levels of the operands in the local state. To
express our security policy, we declare a function $\Gamma(x)$ that assigns to every variable
$x$ a security level. If we now want to \texttt{store} the top of the stack into the variable
$x$ one premise is that the security level of the program point ($se(i)$) \textit{and} the
security level of the value on top of the operand stack is \textit{lower or equal} to the
security level that was assigned by $\Gamma$ to the variable $x$. If this is the case the head
of $LType$ is removed. The $\sqcup$ operator is like a logical 'or', it returns the higher of
the given security values.

>>>>

The idea is to \textit{"track and regulate"}\cite{Zdancewic04} where information flows to
prevent the leak of secret information. The ways on which the information flows
through the system are called channels. Channels that are not indented to transport
information are called covered channels. These covered channels can
be classified into the following categories \cite{Sabelfeld03} (in the following examples $h$ is a secret
variable and $l$ a variable that is plublic):

@@

The notion of confidentiality that is used in most work in the area of information-flow security is \textit{noninterference}.
This policy is defined in various ways but the essence is, that it requires \textit{"that secret information
[do] not affect [the] publicly observable behavior of a system"}\footnote{Even wen the attacker has full access to the
source code of the program.}\cite{Zdancewic04}. For most real world
applications this policy is far too strict, because it forbids useful programs like password checkers.\footnote{A
password checker needs to reveal whether the user input was correct or not.} Approaches that allow
controlled release of information are called declassification. The kinds of declassification are \textit{what}
information is released, \textit{who} released this information, \textit{where} in the system the information
is released and \textit{when} the information is released (c.f. \cite{Sabelfeld05}). For these approaches it is necessary that an
active attacker can only know as much as a passive attacker.

@@

The next thing introduced are the security levels. We assume the attacker
"is" a level $k$. From this assumption we can reduce every set of security levels
w.l.o.g into $\{low, high\}$, where $low < high$, by mapping elements
that are no more sensitive than $k$ to $low$ and all other elements
-- including incomparable ones -- to $high$. It is also assumed, that access
control works correctly (i.e. the attacker can not access $high$ elements
directly).

@@

The \textit{hidden} threads are the ones we have to care about. These contain
obviously high information in the current program point, but have afterwards
instructions that deal with low information. Since the attacker can watch the
low part of the memory, chances are good that he can deduce high information
through looking at changing low outputs. To prevent indirect flows that are introduced by
these hidden threads, the scheduler will be modified to treat these threads
in a special way. This will be done by "hiding" these threads, therefore comes
the name of them.

@@

The security levels in $LType$ are the security levels of the operands in the local state. To
express our security policy, we declare a function $\Gamma(x)$ that assigns to every variable
$x$ a security level. If we now want to \texttt{store} the top of the stack into the variable
$x$ one premise is that the security level of the program point ($se(i)$) \textit{and} the
security level of the value on top of the operand stack is \textit{lower or equal} to the
security level that was assigned by $\Gamma$ to the variable $x$. If this is the case the head
of $LType$ is removed. The $\sqcup$ operator is like a logical "or", it returns the higher of
the given security values.
